Plant-pollintor networks worldwide are composed by the same specific building

### 2021-10-09 Draft/Draft.Rmd
Responses Alf

Yo para esta version lo veo bien. Se puede mejorar la estructura quizas, pero no se si vale la pena ahora.
---

@@

We calculated the frequency of all motifs up to five nodes (see **Figure 1**) for each empirical network, by using the _bmotif_ package [@bmotifsimmons2019]. To control for variation in network [network or subnetwork or mitif? Yo creo que motif, no?]() size, motif frequencies were normalised as a proportion of the total number of motifs within each motif class (i.e., the number of nodes a motif contains). Like @simmons2020, we just used five-node motifs in our analyses for visualisation, interpretation and computational reasons. In addition, we also excluded two-node motifs (or links) from our analyses because their normalised frequencies would always equal one.

@@

Once we obtained $p_i^O$ and $p_i^E$, we used a simulation [IB: Simulation or null model?]() approach to determine whether the former is likely to come from the latter or not. This approach was preferred since the large number of possible motif combinations and the small probabilities for some of them advise against using an exact test of goodness-of-fit or a Chi-square one. Specifically, we created 1,000 random samples with repetition of possible motif combinations, where each sample contained 10 million elements and, for each combination, the probability of being selected was equal to its expected probability. From those random samples, we extracted the mean and the standard deviation of the expected probability of $i$, denoted as $E\left [ p_i^E \right ]$ and $\sigma\left [ p_i^E \right ]$, respectively, and calculated the z-scores of $p_i^O$ as $z_i^O = \left ( p_i^O - E\left [ p_i^E \right ] \right )/\sigma \left [ p_i^E \right ]$, for those motif combinations with $p_i^O > 0$. According to the usual interpretation of z-scores, combinations with $z_i^O > 1.96$ are over-represented, whereas those with $z_i^O < -1.96$ are under-represented, at the 95%  confidence level. Notice that we focused on combinations with $p_i^O > 10^{-7}$ because, beyond the interest that can arouse the combinations that appear at most once, we do not have enough numerical resolution to accurately detect whether or not those combinations are under-represented (due to the limited size [ib: size or possible combinations]() of our random samples).

>>>>

Yo para esta version lo veo bien. Se puede mejorar la estructura quizas, pero no se si vale la pena ahora.

Alf: Probablemente no valga la pena.
---

@@

We calculated the frequency of all motifs up to five nodes (see **Figure 1**) for each empirical network, by using the _bmotif_ package [@bmotifsimmons2019]. To control for variation in network [network or subnetwork or mitif? Yo creo que motif, no? Alf: No, es network. Su tamaño -cantidad de nodos- condiciona las frecuencias posibles de motifs. De hecho, la frase la saqué de los métodos de simmons 2020]() size, motif frequencies were normalised as a proportion of the total number of motifs within each motif class (i.e., the number of nodes a motif contains). Like @simmons2020, we just used five-node motifs in our analyses for visualisation, interpretation and computational reasons. In addition, we also excluded two-node motifs (or links) from our analyses because their normalised frequencies would always equal one.

@@

Once we obtained $p_i^O$ and $p_i^E$, we used a simulation [IB: Simulation or null model? Alf: Yo diría simulación por consistencia con las secciones anteriores, en las que decíamos que habíamos simulado 1,000 redes usando el vaznull de bipartite. Aquí simulamos una muestra de motifs usando las prob. esperadas.]() approach to determine whether the former is likely to come from the latter or not. This approach was preferred since the large number of possible motif combinations and the small probabilities for some of them advise against using an exact test of goodness-of-fit or a Chi-square one. Specifically, we created 1,000 random samples with repetition of possible motif combinations, where each sample contained 10 million elements and, for each combination, the probability of being selected was equal to its expected probability. From those random samples, we extracted the mean and the standard deviation of the expected probability of $i$, denoted as $E\left [ p_i^E \right ]$ and $\sigma\left [ p_i^E \right ]$, respectively, and calculated the z-scores of $p_i^O$ as $z_i^O = \left ( p_i^O - E\left [ p_i^E \right ] \right )/\sigma \left [ p_i^E \right ]$, for those motif combinations with $p_i^O > 0$. According to the usual interpretation of z-scores, combinations with $z_i^O > 1.96$ are over-represented, whereas those with $z_i^O < -1.96$ are under-represented, at the 95%  confidence level. Notice that we focused on combinations with $p_i^O > 10^{-7}$ because, beyond the interest that can arouse the combinations that appear at most once, we do not have enough numerical resolution to accurately detect whether or not those combinations are under-represented (due to the limited size [ib: size or possible combinations. Alf: yo diria size porque el hecho de solo usar 10 millones de elementos en cada muestra nos impide tener la suficiente resolución numérica para valorar la representación de combinaciones con probabilidades de 10e-8 o menores]() of our random samples).
